---
title: "`caRey`"
output:
  github_document:
    toc: true
    toc_depth: 4
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.com/nicholascarey/caRey.svg?branch=master)](https://travis-ci.com/nicholascarey/caRey)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/nicholascarey/caRey?branch=master&svg=true)](https://ci.appveyor.com/project/nicholascarey/caRey)
[![Coverage status](https://codecov.io/gh/nicholascarey/caRey/branch/master/graph/badge.svg)](https://codecov.io/github/nicholascarey/caRey?branch=master)
[![DOI](https://zenodo.org/badge/174339770.svg)](https://zenodo.org/badge/latestdoi/174339770)

The `caRey` package is a collection of R functions. I will add to it periodically ([suggestions welcome](https://github.com/nicholascarey/caRey/issues)). It is not intended to be a fully featured package, more a collection of handy functions. 

If you use it a citation using this [Zenodo DOI](https://zenodo.org/record/3668902) would be much appreciated.

### Installation
`caRey` can be installed using the `devtools` package:

```r
install.packages("devtools")
devtools::install_github("nicholascarey/caRey")
```

### Functions

#### `progress()`

Progress bar function.

```{r echo = F}
library(caRey)
```

```{r eval = F}
## Simple example with custom message

for(i in 1:1000) {
    Sys.sleep(0.01) # pause or it will be too quick
    progress(i, max = 1000, message = "Operation progress")
    }
```

```{r eval = T, echo = F}

    progress(500, max = 1000, message = "Operation progress")
    
```

### Future functionality
In due course I'll add a few more functions. Suggestions for additional functions are welcome via [email](mailto:nicholascarey@gmail.com), or by [opening an issue](https://github.com/nicholascarey/caRey/issues).

### Bug reports
If you find any bugs, weird behaviour, or other issues please [let me know](mailto:nicholascarey@gmail.com) or [open an issue](https://github.com/nicholascarey/caRey/issues).


